CODE CHECK

### 2020-05-29 codecheck-paper.Rmd
Update codecheck-paper.Rmd

- need publishers build up data science experts who can conduct checks?
- integration of software/data citation checks benefitial?
- bot-support and tools (linter)
- Does nudging towards better practices work (highlight the successes) or is any check with opt-in doomed to fail?
- Do we need more than one codechecker? Is there a similar diversity as in a peer review where more opinions are needed?
- can CODE CHECK work for preprints? how? is a re-check required?
- risk: is the hurdle too low? are "levels" of checks are solution to increase transparency of check's level of detail
- code check in the context of innovations and disruptions in scientific publishing
  - https://doi.org/10.1042/ETLS20180172
  - https://doi.org/10.3390/publications7020034
- should every code be checkd, or should the labour be capped by only checking "important" works or at important stages; if yes, isn't peer review such a stage?
- see https://github.com/codecheckers/discussion

>>>>

- need publishers build up data science experts who can conduct checks?
- integration of software/data citation checks benefitial?
- bot-support and tools (linter)
- how can open platforms be used to enable a review in private (cf. https://www.cambridge.org/core/blog/2019/08/19/how-to-make-the-data-and-code-for-your-manuscript-available-to-peer-reviewers-before-making-it-public/), if that is desired
- Does nudging towards better practices work (highlight the successes) or is any check with opt-in doomed to fail?
- Do we need more than one codechecker? Is there a similar diversity as in a peer review where more opinions are needed?
- can CODE CHECK work for preprints? how? is a re-check required?
- risk: is the hurdle too low? are "levels" of checks are solution to increase transparency of check's level of detail
- code check in the context of innovations and disruptions in scientific publishing
  - https://doi.org/10.1042/ETLS20180172
  - https://doi.org/10.3390/publications7020034
- should every code be checkd, or should the labour be capped by only checking "important" works or at important stages; if yes, isn't peer review such a stage?
- see https://github.com/codecheckers/discussion
